Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-11-11 Methods-and-Results.Rmd
typo

In terms of the content of the topics, we find that a number of topics are primarily task-oriented, where participants hope to increase their study, research, presentation, or work performance. Opposing the task and work oriented needs, are a wide variety of leisure-related needs. Specifically, relaxation and entertainment wishes were prominent terms across several topics. Additionally, a number of clusters were primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself. Similarly, socializing and celebrations were also explicit social needs (incl., parties). This also included a subtopic of social spiritual, religious, and otherwise transcendental needs (incl. meditation, prayer, religious services). Among the leisure-oriented topics was also a set of contact goals that were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned inquiry and information needs more generally (e.g., seeking answers, bureaucratic information). A similar set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel related goals in their interactions with the majority group members.

One interesting observation was the importance of contact goals specific to contact through the medical and public health system. This goal type was partly specific to our young medical professionals sample (e.g., working with patients, treatment), but also more broadly interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals). Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members. Another topic less commonly found within the literature were more practically oriented needs, where participants sought to share food and cook together, or had organizational needs (e.g., housing, cleaning, and co-living). In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyper parameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction. The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.

>>>>

In terms of the content of the topics, we find that a number of topics are primarily task-oriented, where participants hope to increase their study, research, presentation, or work performance. Opposing the task and work oriented needs, are a wide variety of leisure-related needs wishes, like relaxation and entertainment. Additionally, some clusters were primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself. Similarly, socializing and celebrations were also explicit social needs (incl., parties). This also included a subtopic of spiritual, religious, and otherwise transcendental needs (incl. meditation, prayer, religious services). Among the leisure-oriented topics was also a set of contact goals that were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned informational needs more generally (e.g., seeking answers, bureaucratic information). A similar set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel related goals in their interactions with the majority group members.

One interesting observation was the importance of contact goals specific to contact through the medical and public health system. This goal type was partly specific to the medical professionals (e.g., working with patients, treatment), but also more broadly interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals). Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members. Another topic less commonly found within the literature were more practically oriented needs, where participants sought to share food and cook together, or had organizational needs (e.g., housing, cleaning, and co-living). In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyper parameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction. The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.

### 2022-11-11 Methods-and-Results.tex
typo

In terms of the content of the topics, we find that a number of topics
are primarily task-oriented, where participants hope to increase their
study, research, presentation, or work performance. Opposing the task
and work oriented needs, are a wide variety of leisure-related needs.
Specifically, relaxation and entertainment wishes were prominent terms
across several topics. Additionally, a number of clusters were primarily
relationship-oriented, so that participants sought contact with outgroup
members for intimate and casual social contact in itself. Similarly,
socializing and celebrations were also explicit social needs (incl.,
parties). This also included a subtopic of social spiritual, religious,
and otherwise transcendental needs (incl.~meditation, prayer, religious
services). Among the leisure-oriented topics was also a set of contact
goals that were specifically migration-specific (e.g., wish to learn
about culture, politics, and language) or were concerned inquiry and
information needs more generally (e.g., seeking answers, bureaucratic
information). A similar set of topics was specifically geared towards a
wish to experience cultural products (e.g., music, theater, food) or had
travel related goals in their interactions with the majority group
members.

One interesting observation was the importance of contact goals specific
to contact through the medical and public health system. This goal type
was partly specific to our young medical professionals sample (e.g.,
working with patients, treatment), but also more broadly interactions of
newcomers with the outgroup majority as patients themselves (e.g.,
therapeutic goals). Also health, fitness, and personal improvement goals
(e.g., sports and music) were common goals that participants shared
during the interactions with the majority group members. Another topic
less commonly found within the literature were more practically oriented
needs, where participants sought to share food and cook together, or had
organizational needs (e.g., housing, cleaning, and co-living). In sum,
almost all extracted topics fall into broader or narrower need concepts
that are commonly discussed within the psychological needs literature
\citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the
migration experience that has remained broadly under-explored
\citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyper parameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction. The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.

>>>>

In terms of the content of the topics, we find that a number of topics
are primarily task-oriented, where participants hope to increase their
study, research, presentation, or work performance. Opposing the task
and work oriented needs, are a wide variety of leisure-related needs
wishes, like relaxation and entertainment. Additionally, some clusters
were primarily relationship-oriented, so that participants sought
contact with outgroup members for intimate and casual social contact in
itself. Similarly, socializing and celebrations were also explicit
social needs (incl., parties). This also included a subtopic of
spiritual, religious, and otherwise transcendental needs
(incl.~meditation, prayer, religious services). Among the
leisure-oriented topics was also a set of contact goals that were
specifically migration-specific (e.g., wish to learn about culture,
politics, and language) or were concerned informational needs more
generally (e.g., seeking answers, bureaucratic information). A similar
set of topics was specifically geared towards a wish to experience
cultural products (e.g., music, theater, food) or had travel related
goals in their interactions with the majority group members.

One interesting observation was the importance of contact goals specific
to contact through the medical and public health system. This goal type
was partly specific to the medical professionals (e.g., working with
patients, treatment), but also more broadly interactions of newcomers
with the outgroup majority as patients themselves (e.g., therapeutic
goals). Also health, fitness, and personal improvement goals (e.g.,
sports and music) were common goals that participants shared during the
interactions with the majority group members. Another topic less
commonly found within the literature were more practically oriented
needs, where participants sought to share food and cook together, or had
organizational needs (e.g., housing, cleaning, and co-living). In sum,
almost all extracted topics fall into broader or narrower need concepts
that are commonly discussed within the psychological needs literature
\citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the
migration experience that has remained broadly under-explored
\citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyper parameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction. The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
